Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-08 batchdedup/scheduling.tex
added proof for basic round packing algorithm

A1 significantly improves our simulated results, also bringing our CoW costs
much closer to the best case than the worst case, as can be seen in
Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
focuses on the deduplication and so doesn't make use of CoW, but we can see
that our simulated times closely match measured runtimes (hopefully). \todo{I
haven't actually implemented the schedulers into the dedup yet to test this}

>>>>

A1 significantly improves our simulated results, also bringing our CoW costs
much closer to the best case than the worst case, as can be seen in
Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
focuses on the deduplication and so doesn't make use of CoW, but we can see
that our simulated times closely match measured runtimes (hopefully).

\subsection{Standard Bin Packing Heuristic}
\todo{this section might need to be moved around and/or broken up. also, notation might still need to be adjusted. }
\begin{figure}
\begin{lstlisting}[frame=single]
bpl:
for each Machine m
  sort VMs in descending order by size
  while there is an unscheduled VM
    pick the first unscheduled VM a
    pick the round b with the least
      amount of VM data for m
    schedule VM a to round b
Halt
\end{lstlisting}
\caption{Round packing heuristic}
\end{figure}

Using the above algorithm we can show that for any round $r$, the amount of
data scheduled to $r$ across all VMs has the upper bound of twice the optimal
amount of data for a perfectly balanced schedule (i.e. the worst case for any
round is bounded by twice the best case).

Proof:
first we define $load(m,r)$ to be the amount of data from VMs on Machine $m$
to round $r$, $Machines$ to be the set of all machines, and $Rounds$ to be
the set of all rounds.
now define $2b_m$ to be the upper bound for data backuped up in a single round, 
where 
%$b_m = min(\frac{\sum \left\{ {x \mid x \in {VMS}_m} \right\}}{\left\vert\ {Rounds} \right\vert}, largest~VM~on~m)$,
$b_m = min(\frac{\sum \left\{ {VMs~on~m} \right\}}{\left\vert {Rounds} \right\vert}, largest~VM~on~m)$,
and $2b$ to be the global upper bound for each round, where
$b = \sum \left\{ b_m | m \in Machines \right\}$. We would like to prove the
actual global load is less than $2b$. we will do this by proving that for
each machine $2b_m$ is the upper bound, which from the definition of $b$ can be
extended to a global uppoer bound of $2b$. More formally, we would like to show:

\[
    (\forall m \in Machines, \forall r \in Rounds) load(m,r) < 2b_m
\]

Now let $x$ be a VM from Machine $m$ to be scheduled.
For each round $r$ there are two possibilities:
\begin{itemize}
    \item $load(m,r) < b_m \Longrightarrow$
        $load(m,r)+x < b_m+x$
    \item $load(m,r) \ge b_m \Longrightarrow$

        $(\exists k \in Rounds) load(m,k) < b_m$
\end{itemize}

since we never schedule to a round where $load(m,r) \ge b_m$, $load(m,r)$ must
be less than $b_m+x$, where $x$ is the largest VM on $m$. By Definition
$b_m > x$, so
$load(m,r) < 2b_m$ for each machine, and therefore the global load for each
round is less than $2b$.
The expected case can be improved though by
packing the largest VMs first and always scheduling to the round with the least
data.
